Identification and performance of stock-recruitment functions in state

### 2024-02-06 Ecov_study/recruitment_functions/presentation/SRR_presentation.Rmd
adding acknowledgement

- This work could not have been completed without the use of Azure computing (NOAA) and MIT (... greg to fill in)
- We thank other members of the SSRTWG for thoughtful comments during earlier discussions and presentations of this work

>>>>

- This work could not have been completed without the use of Azure computing (NOAA) and the MIT engaging cluster (courtesy of Chris Hill)
- We thank other members of the SSRTWG for thoughtful comments during earlier discussions and presentations of this work
